Notes on Wide Gap

### 2016-06-15 paper/wide_gap_notes.tex
code to make movies of thin gap simulations
different streamfunction equations added (for hmri/smri case) to widegap notes

@@

-- In the ideal thin-gap case, V = constant, and thus invariant under parity. Walls and boundary conditions impose symmetric and antisymmetric states.

@@

>>>>

\section{Equations in more succinct form}

Defining the stream functions instead as

\begin{equation}
  \label{eq:stokes}
  \mathbf{u} \, = \, \left[\begin{matrix}
\partial_z \psi\ \rhat\\
\uphi \ \phihat\\
- \partial_r^* \psi\ \zhat\\
\end{matrix}\right]
\end{equation}

where $\partial_r^* = \partial_r + \frac{1}{r}$

And defining the function $D^2 = \nabla^2 - \frac{1}{r^2}$

We obtain a very compact form for the equations. The following include helical MRI terms, and reduce to the SMRI when $\xi \rightarrow 0$.

\beq
\partial_t D^2 \Psi - \frac{2}{r}u_0\partial_z u_\phi - \frac{2}{\beta} B_0 \partial_z D^2 A + \frac{2}{\beta} \frac{2}{r^2} \xi B_0 \partial_z B_\phi - \frac{1}{\reye} D^4 \Psi = 0
\eeq

\beq
\partial_t u_\phi + \frac{1}{r} u_0 \partial_z \Psi + \partial_r u_0 \partial_z \Psi - \frac{2}{\beta} B_0 \partial_z B_\phi - \frac{1}{\reye} D^2 u_{\phi} = 0
\eeq

\beq
\partial_t A - B_0 \partial_z \Psi - \frac{1}{\reym} D^2 A = 0
\eeq

\beq
\partial_t B_\phi + \frac{1}{r}u_0 \partial_z A - B_0 \partial_z u_\phi - \partial_r u_0 \partial_z A - \frac{2}{r^2} \xi B_0 \partial_z \Psi - \frac{1}{\reym} D^2 B_\phi = 0
\eeq

@@

-- In the ideal thin-gap case, V = constant, and thus solutions must be eigenstates of parity. Walls and boundary conditions impose symmetric and antisymmetric states.

@@

Channel modes:
-- exact nonlinear solutions in local approximation,
